### 2018-05-06 papers/synth/experiments.tex
as

@@

    plos1-dia & 0.041&$\infty$& 0.320 &$\infty$& 0.225 & $\infty$ & 0.33&$\infty$& 3.74 & del: . 1 edge, 1 edge bit 1 node, 1 act each add: 1 edge bit 1 node bit\\\hline
    plos2-dia & 3.97 & 0 &  2.647 & 0  & 5.941 & 0 & 5.680 & 0 & 3.56 & 0 \\\hline
    mukund  & 3.483 & 1 edge  & 4.379 & 5 edge bits  & 6.340[-] / 29.980 & 2 edge, 10 edge bits  & 10.4052[-] & [-] & 3.650  &  del : 1 edge, 2 edge bit, 1 active node. add:1 edge 4 edge bit 4 node bit, 2 act \\\hline
    node4  & 4.1502  & 1 edge  & 10.562  & 12 mol & 3.401  & $\infty$ & 4.760 &$\infty$&  5.05  & del: 2 edge, 2 act, 1 node and 1 act. add: 12 node, 8 edge, 1 edge bits \\\hline
    yeast-graph & 40.8728  & 1 edge  &   timeout  & N/A   & 1313.91  & 1 edge  & 517.619   & 1 edge    & 380.43  &  del: 1 edge, 2 node, 2 act bits each. add: 2 edge, 12 mol, 7 node bits \\\hline
    mukund-comp   & 0.0    & 0.0    & 0.0    & 0.0    & 0.0         & 0.0      & 0.0   & 0.0    & 0.0    & 0.0\\\hline
  \end{tabular}
  \caption{Run-times for searching for Z3 models (in secs). \#C  stands for minimum changes.
  Time is reported in seconds.}
  \label{tab:z3-qf-graph}
\end{table}

@@

The table shows timing for various synthesis queries.
%
For each synthesis query, we have two columns.
%
One column reports the timing and the other reports the minimum changes
needed to obtain a valid VTS.
%
$\infty$ indicates that any number of changes with the synthesis query
search space can obtain the VTS.
%
%\ashu{@ankit: please discuss all the synthesis queries in the table.}
In the table, we are reporting five synthesis queries
%
The first one only adds new labelled edges to the graph.
%
We have ranked the all possible graph edits with the simple rank of
minimum updates.
%
Our tools were able to complete the graphs by adding five new edges
and nine new molecules in 210s.
%
The second query adds new labels to the edge and was able to
fix the graphs with eleven new molecule labels in 180s.
%
The third query synthesizes NNF Boolean functions only containing
$\land$ and $\lor$ gates.
%
The result shows the basic template of 4 leaves and 3 gates we allow
the user to provide its own template in our front-end language.
%
The tool was able to synthesize the Boolean functions in 470s.
%
To illustrated the versatility of our tool,
the the fourth query synthesizes $3$-CNF functions (encoding not presented) and was able
to synthesis the results for all graphs in 500s.
%
Finally, we report queries that allows both addition and deletion of parts of
VTS\ashu{which parts}. 
%
%Our experiments suggest that the synthesis problems are solvable by modern 
%solvers and the synthesis technology may be useful for biological research.
%

>>>>

\begin{landscape}
\begin{table}[t]
  \centering
  \begin{tabular}[t]{|c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|}\hline
    {\multirow{2}{*} \textbf{}}  & \multicolumn{2}{c|}{\textbf{Add}} & \multicolumn{2}{c|}{\textbf{Add}} & \multicolumn{2}{c|}{\textbf{Learning NNF}}  &  \multicolumn{2}{c|}{\textbf{Learning}} &  \multicolumn{2}{c|}{\textbf{Add/Delete}} \\
    {\multirow{2}{*} \textbf{Benchmark}}  & \multicolumn{2}{c|}{\textbf{edge}} & \multicolumn{2}{c|}{\textbf{molecules}} & \multicolumn{2}{c|}{\textbf{(only $\land$ and $\lor$)}}  &  \multicolumn{2}{c|}{\textbf{k-CNF}} &  \multicolumn{2}{c|}{\textbf{parts}} \\
    \cline{2-11}
    {} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} \\
    \hline

@@

    plos1-dia & 0.041&$\infty$& 0.320 &$\infty$& 0.225 & $\infty$ & 0.33&$\infty$& 3.74 & del: . 1 edge, 1 edge bit 1 node, 1 act each add: 1 edge bit 1 node bit\\\hline
    plos2-dia & 3.97 & 0 &  2.647 & 0  & 5.941 & 0 & 5.680 & 0 & 3.56 & 0 \\\hline
    mukund  & 3.483 & 1 edge  & 4.379 & 5 edge bits  & 6.340[-] / 29.980 & 2 edge, 10 edge bits  & 10.4052[-] & [-] & 3.650  &  del : 1 edge, 2 edge bit, 1 active node. add:1 edge 4 edge bit 4 node bit, 2 act \\\hline
    node4  & 4.1502  & 1 edge  & 10.562  & 12 mol & 3.401  & $\infty$ & 4.760 &$\infty$&  5.05  & del: 2 edge, 2 act, 1 node and 1 act. add: 12 node, 8 edge, 1 edge bits \\\hline
    yeast-graph & 40.8728  & 1 edge  &   timeout  & N/A   & 1313.91  & 1 edge  & 517.619   & 1 edge    & 380.43  &  del: 1 edge, 2 node, 2 act bits each. add: 2 edge, 12 mol, 7 node bits \\\hline
    mukund-comp   & 0.0    & 0.0    & 0.0    & 0.0    & 0.0         & 0.0      & 0.0   & 0.0    & 0.0    & 0.0\\\hline
  \end{tabular}
  \caption{Run-times for searching for Z3 models (in secs). \#C  stands for minimum changes.
  Time is reported in seconds.}
  \label{tab:z3-qf-graph}
\end{table}
\end{landscape}

@@

The table shows timing for various synthesis queries.
%
For each synthesis query, we have two columns.
%
One column reports the timing and the other reports the minimum changes
needed to obtain a valid VTS.
%
$\infty$ indicates that any number of changes with the synthesis query
search space can obtain the VTS.
%
%\ashu{@ankit: please discuss all the synthesis queries in the table.}
In the table, we are reporting five synthesis queries
%
The first one only adds new labelled edges to the graph.
%
We have ranked the all possible graph edits with the simple rank of
minimum updates.
% %
% Our tools were able to complete the graphs by adding five new edges
% and nine new molecules in 210s.
%
The second query adds new labels to the edge.
%  and was able to
% fix the graphs with eleven new molecule labels in 180s.
%
The third query synthesizes NNF Boolean functions only containing
$\land$ and $\lor$ gates for activity functions, while allowing
more edges to be added.
%
The result shows the basic template of 4 leaves and 3 gates.
%
% The tool was able to synthesize the Boolean functions in 470s.
%
To illustrated the versatility of our tool, the the fourth query
synthesizes $3$-CNF functions (encoding not presented).
%  and was able to
% synthesis the results for all graphs in 500s.
%
Finally, we report queries that allows both addition and deletion of parts of
VTS\ashu{which parts}. 
%
%Our experiments suggest that the synthesis problems are solvable by modern 
%solvers and the synthesis technology may be useful for biological research.
%
